---
title: "pagerank_wikivote"
output: html_document
---
PageRank is a popular algorithm in scoring nodes importance in a graph dataset.
Here is an example of applying pagerank algorithm to wiki-administrators-vote data to find out:
Who are important wiki administrators involved in elections? 

First of all, let's analyze the dataset.
data souce: https://snap.stanford.edu/data/wiki-Vote.txt.gz
Source (citation)

    J. Leskovec, D. Huttenlocher, J. Kleinberg. Signed Networks in Social Media. CHI 2010.
    J. Leskovec, D. Huttenlocher, J. Kleinberg. Predicting Positive and Negative Links in Online Social Networks. WWW 2010.

Here displays some information in the data source:

```{r}
wikivote = "/Users/lulu/BIGDATA/NetworkX/wiki-Vote.txt"
read.csv(wikivote,nrow = 3)
```

As you can see, the dataset is very similar to a graph type data structure, since there are only two elements in each line, showing a vote from A to B. 
In R, the 'igraph' library provides function make_graph to convert a vector to a graph object which is then suitable as the input of the function page.rank. The page.rank function gives the score of importance of each node using google pagerank algorithm.

```{r}
dat = read.csv(wikivote,sep ='\t',skip = 3)
edges = as.character(as.vector(as.matrix(dat)))
library(igraph)
graf = make_graph(edges,directed = TRUE)
prank = page.rank(graf,directed = TRUE,vids = V(graf))
```

Now we have IDs of the top 10 important/popular administrators as well as their scores.

```{r, echo=FALSE}
head(sort(prank$vector,decreasing = TRUE),10)
```

The library igraph is also available in python. 
There is another similar library NetworkX in python which also does a very good job in dealing with graph data.
